---
title: "Carl's Demo R Notebook"
output: html_notebook
---

I use the following chunk of code to load the data and libraries.  Note the 
green progress bar.

```{r setup}
library(ttbbeer)
library(lubridate)
library(dplyr)
library(tidyr)

beermaterials$mon <- rep(1:12,10)
beermaterials$time <- as.Date(paste(beermaterials$Year, beermaterials$mon, "01", sep="-"))

hop_prices <- data.frame(
  time = as.Date(paste(2005:2015, "12", "31", sep="-")),
  price = c(1.94, 2.05, 2.99, 4.03, 3.57, 3.28, 3.14, 3.17, 3.35, 3.67, 4.38)
)
```

```{r checking the data}
summary(beermaterials)

summary(hop_prices)
```

As a homebrewer, I am interested in the form of hops used by US breweries.  So
here is a quick chart to show the two forms of hops in the data.

As is, the chart isn't too informative, so I will log the vertical axis.

```{r first chart}
beermaterials %>% 
  select(time, Dry = Hops_dry, Extract = Hops_extracts) %>% 
  gather(Hops, Pounds, -time) %>% 
  mutate(
    Pounds = Pounds / 1e6
  ) %>% 
  ggplot(aes(x=time, y=Pounds, color=Hops)) +
    geom_line() +
    theme_minimal() + 
    labs(x = "", y = "Pounds (millions)", 
         title="Trends in the form of hops used by US breweries",
         caption="Sources: ttbbeer::beermaterials") + 
    theme(legend.position="bottom")

```

There is a sharp decline in the amount of dry hops used beginning in the middle
of 2013. Part of this could be a change in data collection practicies (especially
given the two large spikes that correspond to the end of 2014 and 2015), but 
what about other explanations.

## Possible explanations

I know from reading that the price of hops has increased substantially in the last
few years. So lets plot those data on a similar time scale. **Demo**

```{r second chart}
hop_prices %>% 
  ggplot(aes(x=time, y=price)) + 
    geom_line() +
    theme_minimal() + 
    labs(x = "", y = "Dollars/Pound", 
         title="Trends in the price of hops in the US",
         caption="Sources: https://ycharts.com/indicators/us_hops_price_received") 
```

## Live updating

**DEMO**

## New run options
