---
title: "Using `R` Notebooks"
author: "Carl Frederick"
date: "August 17, 2016"
output: 
  revealjs::revealjs_presentation:
    theme: simple
    transition: slide
    center: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)


```

## Why Notebooks?

```{r}
library(DiagrammeR)

DiagrammeR("
  graph LR;
    A(<h1>Reproducible Research</h1>)-->C(<h1>R Notebooks</h1>);
    B(<h1>Simplified Interaction</h1>)-->C;
", width=1000, height=400)

```

## Other Notebook platforms?

- Jupyter <http://jupyter.org/>
- IPython (old, superseded by Jupyter)
    
    
## Notebook alternatives:

- R markdown documents
- knitr / Sweave
- Word + cut/paste :(

---

<h1>DEMO</h1>

## Key Capabilities

>- Shareable (download .Rmd file via browser)
>- Code folding in the browser
>- Runs in the current environment
>- No need to re-render the entire document when code changes
>- Can incorporate multiple languages (Python, Perl, C)
>- Seemlessly convert to regular .Rmd file with typical outputs

## Cons

>- Remember to run the chunks before you preview ... or else they won't 
update in the .nb.html file.
>- Just different enough from `R` markdown that little things can trip you up.

## Thanks

- carl.frederick@dpi.wi.gov
- RStudio preview version: <https://www.rstudio.com/products/rstudio/download/preview/>
- R Notebooks webinar: <https://www.rstudio.com/resources/webinars/introducing-notebooks-with-r-markdown/>

## Version info: 
```{r thanks, eval=TRUE}
cat(paste("RStudio Version: 0.99.1258\n\n"))
sessionInfo()
```

